Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-10-16 ms.tex
added a few notes on the CV3 tests.

As with the spatial scanning mode on HST \citep[e.g.][]{}, spreading the light of a source over many pixels can improve the precision

NIRCam instrument was 
 package (was lowered into

Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images used the Crogenic Vacuum 3 (CV3) stability tests.

@@

>>>>

As with the spatial scanning mode on HST \citep[e.g.][]{mccullough2012spatialScan,demin13}, spreading the light of a source over many pixels can improve the precision of spectroscopy.
This is also accomplished by ground-based observatories by either de-focusing the telescope \citep{southworth2009defocusing} or by employing a beam-shaping diffuser \citep{stefansson2017diffusers}.
By spreading the light source over many pixels, the light curve becomes less sensitive to flat fielding or intra-pixel sensitivity errors with the jitter or seeing variations during an observation.
Similarly, NIRCam can employ a weak lens to defocus a star's light.
Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images during the CV3 stability tests.
The hexagonal PSF is summed with circular aperture with a radius of 70 pixels.
The central peak may used to find a centroid of the star and center the circular aperture.

@@

A series of detector stability tests was performed using this +8 wave weak lens and 1.55 $\mu$m LED in a few different modes.
